Chapter 2 Draft

### 2020-05-04 Rmd/Draft.tex

\documentclass[12pt,]{article}
\usepackage{lmodern}
\usepackage{amssymb,amsmath}
\usepackage{ifxetex,ifluatex}
\usepackage{fixltx2e} % provides \textsubscript
\ifnum 0\ifxetex 1\fi\ifluatex 1\fi=0 % if pdftex
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
\else % if luatex or xelatex
  \ifxetex
    \usepackage{mathspec}
  \else
    \usepackage{fontspec}
  \fi
  \defaultfontfeatures{Ligatures=TeX,Scale=MatchLowercase}
\fi
% use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
% use microtype if available
\IfFileExists{microtype.sty}{%
\usepackage[]{microtype}
\UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\PassOptionsToPackage{hyphens}{url} % url is loaded by hyperref
\usepackage[unicode=true]{hyperref}
\hypersetup{
            pdftitle={Chapter 2 Draft},
            pdfborder={0 0 0},
            breaklinks=true}
\urlstyle{same}  % don't use monospace font for urls
\usepackage[margin=1in]{geometry}
\usepackage{graphicx,grffile}
\makeatletter
\def\maxwidth{\ifdim\Gin@nat@width>\linewidth\linewidth\else\Gin@nat@width\fi}
\def\maxheight{\ifdim\Gin@nat@height>\textheight\textheight\else\Gin@nat@height\fi}
\makeatother
% Scale images if necessary, so that they will not overflow the page
% margins by default, and it is still possible to overwrite the defaults
% using explicit options in \includegraphics[width, height, ...]{}
\setkeys{Gin}{width=\maxwidth,height=\maxheight,keepaspectratio}
\IfFileExists{parskip.sty}{%
\usepackage{parskip}
}{% else
\setlength{\parindent}{0pt}
\setlength{\parskip}{6pt plus 2pt minus 1pt}
}
\setlength{\emergencystretch}{3em}  % prevent overfull lines
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
\setcounter{secnumdepth}{0}
% Redefines (sub)paragraphs to behave more like sections
\ifx\paragraph\undefined\else
\let\oldparagraph\paragraph
\renewcommand{\paragraph}[1]{\oldparagraph{#1}\mbox{}}
\fi
\ifx\subparagraph\undefined\else
\let\oldsubparagraph\subparagraph
\renewcommand{\subparagraph}[1]{\oldsubparagraph{#1}\mbox{}}
\fi

% set default figure placement to htbp
\makeatletter
\def\fps@figure{htbp}
\makeatother

\usepackage{setspace}\doublespacing
\usepackage{booktabs}
\usepackage{longtable}
\usepackage{array}
\usepackage{multirow}
\usepackage{wrapfig}
\usepackage{float}
\usepackage{colortbl}
\usepackage{pdflscape}
\usepackage{tabu}
\usepackage{threeparttable}
\usepackage{threeparttablex}
\usepackage[normalem]{ulem}
\usepackage{makecell}
\usepackage{xcolor}

\title{Chapter 2 Draft}
\author{}
\date{\vspace{-2.5em}}

@@

\section{Abstract (draft)}\label{abstract-draft}

@@

\blandscape

\begin{tabular}{r|l|r|l|l|l|l|l|r|r|r|l|l|l}
\hline
X & BIBTEXKEY & Id\_number & longitude & latitude & country & experiment\_year & unique\_networks & plant\_species & pollinator\_species & network\_size & Sampling\_method & Sampling\_zoo\_phytocentric & Data\_type\\
\hline
1 & 1\_metaweb\_carpobrotus\_Bartomeus\_2008 & 1 & 3.296797 & 42.315336 & Spain & 2005 & 3 & 18 & 37 & 666 & Plots 50*50m with 2 transects (N=3) & Phytocentric & Quantitative\\
\hline
2 & 10\_metaweb\_fang\_huang\_2012 & 10 & 99.63806 & 27.90139 & China & 2008-2010 & 3 & 130 & 247 & 32110 & plots with stratified distribution to include rare plants within 800*250m plot & Phytocentric & Quantitative\\
\hline
3 & 11\_metaweb\_inouye\_1990 & 11 & 135.866667 & 35.166667 & Japan & 1984-1987 & 4 & 114 & 883 & 100662 & Transect from stream and a bog & Phytocentric & Quantitative\\
\hline
4 & 12\_inouye\_1988 & 12 & 148.266667 & -36.45 & Australia & 1983-1984 & 1 & 40 & 85 & 3400 & 26 plots with stratified sampling of 10 minutes in each site & Phytocentric & Quantitative\\
\hline
5 & 13\_metaweb\_kaiser\_bunbury\_2009 & 13 & 57.443254 & -20.452076 & Republic of Mauritius & 2003-2004 & 2 & 96 & 184 & 17664 & 2h per sepecies within a 330*100m plot & Phytocentric & Quantitative\\
\hline
6 & 14\_metaweb\_kaiser\_bunbury\_2014 & 14 & 55.43333 & -4.666667 & Republic of Seychelles & 2007-2008 & 6 & 37 & 341 & 12617 & 2 to 4 transects of 100m, 48 networks in 6 different sites & Phytocentric & Quantitative\\
\hline
7 & 15\_metaweb\_kato\_2000 & 15 & 129.493741 & 28.377248 & Japan & 1996-1999 & 16 & 110 & 609 & 66990 & Transects from a fixed point from forest or meadow with 10 min per site & Phytocentric & Quantitative\\
\hline
8 & 16\_kevan\_1970 & 16 & -71.3 & 81.816667 & Canada & 1967 & 1 & 20 & 91 & 1820 & random walks & Phytocentric & Qualitative\\
\hline
9 & 17\_lundgren\_2005 & 17 & -52 & 71 & Greenland & 2002 & 1 & 17 & 26 & 442 & 20 mins per spp, regular walks within the plot (100*100m), max per spp 4h & Phytocentric & Quantitative\\
\hline
10 & 18\_olesen\_2002\_mauritius & 18 & 57.43 & -20.25 & Republic of Mauritius & 1998-1999 & 1 & 17 & 26 & 442 & 37 quadrats 100*100m & Phytocentric & Quantitative\\
\hline
11 & 19\_mcmullen\_1993 & 19 & -90.600747 & -0.290164 & Ecuador & NA & All islands & 105 & 54 & 5670 & Metaweb from the literature & Phytocentric & Qualitative\\
\hline
12 & 2\_metaweb\_opuntia\_Bartomeus\_2008 & 2 & 3.296797 & 42.315336 & Spain & 2005 & 3 & 13 & 37 & 481 & Plots 50*50m with 2 transects (N=3), Plots 50*50m (N=3) & Phytocentric & Quantitative\\
\hline
13 & 20\_metaweb\_arthurs\_pass\_primack\_1983 & 20 & 171.566667 & -42.95 & New Zealand & 1976-1978 & 1 & 18 & 60 & 1080 & Random census walks & Phytocentric & Qualitative\\
\hline
14 & 21\_metaweb\_cass\_primack\_1983 & 21 & 171.78466 & -43.02823 & New Zealand & 1976-1978 & 1 & 41 & 139 & 5699 & Random census walks & Phytocentric & Qualitative\\
\hline
15 & 22\_metaweb\_craigieburn\_primack\_1983 & 22 & 171.720224 & -43.099531 & New Zealand & 1976-1978 & 1 & 49 & 118 & 5782 & Random census walks & Phytocentric & Qualitative\\
\hline
16 & 23\_ramirez\_1989 & 23 & -61.716667 & 5.583333 & Venezuela & NA & 1 & 48 & 49 & 2352 & Random census walks & Phytocentric & Qualitative\\
\hline
17 & 24\_metaweb\_ramirez\_1992 & 24 & -67.416667 & 8.933333 & Venezuela & 1983,1984,1989 & 1 & 28 & 53 & 1484 & Random census walks, 16 to 20h of sampling per spp & Phytocentric & Qualitative\\
\hline
18 & 25\_metaweb\_robertson\_1929 & 25 & -89.8968771 & 39.278958 & United States & 1997-1899 & NA & 456 & 1044 & 476064 &  & Phytocentric & Qualitative\\
\hline
19 & 26\_small\_1976 & 26 & -75.5 & 45.4 & Canada & 1973 & 1 & 13 & 34 & 442 & 10 hours per spp & Phytocentric & Quantitative\\
\hline
20 & 27\_chaco\_souza\_2018 & 27 & -57.885 & -21.701111 & Brazil & 2008-2009 & 1 & 62 & 89 & 5518 & 37 plots, 15*25m (at least 50m away), spp within the plots depending sampling effort on abundance & Phytocentric & Quantitative\\
\hline
21 & 28\_metaweb\_traveset\_2013 & 28 & -91.012863 & -0.6907 & Ecuador & 2010-2011 & 1 & 60 & 220 & 13200 & Random census walks with a total of 518h & Phytocentric & Quantitative\\
\hline
22 & 29\_metaweb\_bartomeus\_unpublished\_data\_2015 & 29 & -6.16895, -6.304244, -6.280883, -6.371844, -6.43311, -6.428801, -6.555233, -6.555236, -6.506789, -6.761136, -6.660927, -6.667992, -6.680852, -6.752456, -6.675026, -6.222871 & 37.234966, 37.21781, 37.23919, 37.214279, 37.289861, 37.247223, 37.282079, 37.233157, 37.123856, 37.194957, 37.249254, 37.331447, 37.405047, 37.291937, 37.288346, 37.291091 & Spain & 2015 & 16 & 57 & 277 & 15789 & Transects & Phytocentric & Quantitative\\
\hline
23 & 3\_bek\_2006 & 3 & 10.216667 & 56.066667 & Denmark & 2003 & 1 & 37 & 225 & 8325 & Plots 1*1 in 1 ha & Phytocentric & Qualitative\\
\hline
24 & 30\_olesen\_2002\_azores & 30 & -31 & 39.4 & Azores & 2000 & 1 & 10 & 12 & 120 & 33 quadrats 100*100m & Phytocentric & Quantitative\\
\hline
25 & 4\_bundgaard\_2003 & 4 & 10.233333 & 56.066667 & Denmark & 2003 & 1 & 16 & 44 & 704 & Plots 1*1m near the trail & Phytocentric & Qualitative\\
\hline
26 & 5\_metaweb\_chacoff\_2011 & 5 & -68.015892 & -32.008985 & Argentina & 2006-2009 & 4 & 59 & 196 & 11564 & 4plots-1ha & Phytocentric & Quantitative\\
\hline
27 & 6\_metaweb\_dicks\_2002 & 6 & 1.575532; 1.097873 & 52.762395; 52.413173 & England & 2001? & 2 & 23 & 80 & 1840 & 4plots-1ha & Phytocentric & Quantitative\\
\hline
28 & 7\_metaweb\_dupont\_2009 & 7 & 9.1; 9.266667 & 56.1; 56.066667 & Denmark & 2005 & 2 & 31 & 329 & 10199 & 1*1m within 100*500m plot & Phytocentric & Quantitative\\
\hline
29 & 8\_elberling\_1999 & 8 & 18.5 & 68.35 & Sweden & 1994 & 1 & 24 & 118 & 2832 & Transects within plot of 30*50m & Phytocentric & Quantitative\\
\hline
30 & 9\_dupont\_2009\_zackenberg & 9 & -20.5 & 74.5 & Greenland & 1996-1997 & 1 & 31 & 76 & 2356 & Observation by random census walks within 25 ha & Phytocentric & Qualitative\\
\hline
\end{tabular}

\elandscape

@@

\newpage
*

*PLOT 2**

@@

\section*{REFERENCES}\label{references}
\addcontentsline{toc}{section}{REFERENCES}

\hypertarget{refs}{}
\hypertarget{ref-noreika2019pollinator}{}
Noreika, Norbertas, Ignasi Bartomeus, Marie Winsa, Riccardo Bommarco,
and Erik Öckinger. 2019. ``Pollinator Foraging Flexibility Mediates
Rapid Plant-Pollinator Network Restoration in Semi-Natural Grasslands.''
\emph{Scientific Reports} 9 (1). Nature Publishing Group: 1--11.

>>>>

\documentclass[12pt,]{article}
\usepackage{lmodern}
\usepackage{amssymb,amsmath}
\usepackage{ifxetex,ifluatex}
\usepackage{fixltx2e} % provides \textsubscript
\ifnum 0\ifxetex 1\fi\ifluatex 1\fi=0 % if pdftex
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
\else % if luatex or xelatex
  \ifxetex
    \usepackage{mathspec}
  \else
    \usepackage{fontspec}
  \fi
  \defaultfontfeatures{Ligatures=TeX,Scale=MatchLowercase}
\fi
% use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
% use microtype if available
\IfFileExists{microtype.sty}{%
\usepackage{microtype}
\UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\usepackage[margin=1in]{geometry}
\usepackage{hyperref}
\hypersetup{unicode=true,
            pdftitle={Chapter 2 Draft},
            pdfborder={0 0 0},
            breaklinks=true}
\urlstyle{same}  % don't use monospace font for urls
\usepackage{graphicx,grffile}
\makeatletter
\def\maxwidth{\ifdim\Gin@nat@width>\linewidth\linewidth\else\Gin@nat@width\fi}
\def\maxheight{\ifdim\Gin@nat@height>\textheight\textheight\else\Gin@nat@height\fi}
\makeatother
% Scale images if necessary, so that they will not overflow the page
% margins by default, and it is still possible to overwrite the defaults
% using explicit options in \includegraphics[width, height, ...]{}
\setkeys{Gin}{width=\maxwidth,height=\maxheight,keepaspectratio}
\IfFileExists{parskip.sty}{%
\usepackage{parskip}
}{% else
\setlength{\parindent}{0pt}
\setlength{\parskip}{6pt plus 2pt minus 1pt}
}
\setlength{\emergencystretch}{3em}  % prevent overfull lines
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
\setcounter{secnumdepth}{0}
% Redefines (sub)paragraphs to behave more like sections
\ifx\paragraph\undefined\else
\let\oldparagraph\paragraph
\renewcommand{\paragraph}[1]{\oldparagraph{#1}\mbox{}}
\fi
\ifx\subparagraph\undefined\else
\let\oldsubparagraph\subparagraph
\renewcommand{\subparagraph}[1]{\oldsubparagraph{#1}\mbox{}}
\fi

%%% Use protect on footnotes to avoid problems with footnotes in titles
\let\rmarkdownfootnote\footnote%
\def\footnote{\protect\rmarkdownfootnote}

%%% Change title format to be more compact
\usepackage{titling}

% Create subtitle command for use in maketitle
\providecommand{\subtitle}[1]{
  \posttitle{
    \begin{center}\large#1\end{center}
    }
}

\setlength{\droptitle}{-2em}

  \title{Chapter 2 Draft}
    \pretitle{\vspace{\droptitle}\centering\huge}
  \posttitle{\par}
    \author{}
    \preauthor{}\postauthor{}
    \date{}
    \predate{}\postdate{}

\usepackage{booktabs}
\usepackage{longtable}
\usepackage{array}
\usepackage{multirow}
\usepackage{wrapfig}
\usepackage{float}
\usepackage{colortbl}
\usepackage{pdflscape}
\usepackage{tabu}
\usepackage{threeparttable}
\usepackage{threeparttablex}
\usepackage[normalem]{ulem}
\usepackage{makecell}
\usepackage{xcolor}

\usepackage{setspace}\doublespacing

@@

\#Abstract (draft)

@@

\begin{landscape}

\begingroup\fontsize{7}{9}\selectfont

\begin{longtabu} to \linewidth {>{\raggedright}X>{\raggedright}X>{\raggedright}X>{\raggedright}X>{\raggedright}X>{\raggedright}X>{\raggedleft}X>{\raggedleft}X>{\raggedleft}X>{\raggedright}X>{\raggedright}X>{\raggedright}X}
\toprule
Id & Longitude & Latitude & Country & Year & Networks & Plant spp & Pollinator spp & Network size & Sampling method & Sampling & Data type\\
\midrule
\endfirsthead
\multicolumn{12}{@{}l}{\textit{(continued)}}\\
\toprule
Id & Longitude & Latitude & Country & Year & Networks & Plant spp & Pollinator spp & Network size & Sampling method & Sampling & Data type\\
\midrule
\endhead
\
\endfoot
\bottomrule
\endlastfoot
\rowcolor{gray!6}  Bartomeus 2008 & 3.296797 & 42.315336 & Spain & 2005 & 3 & 18 & 37 & 666 & Plots with transects & Phytocentric & Quantitative\\
\addlinespace
Fang 2012 & 99.63806 & 27.90139 & China & 2008-2010 & 3 & 130 & 247 & 32110 & Plots & Phytocentric & Quantitative\\
\addlinespace
\rowcolor{gray!6}  Inouye 1990 & 135.866667 & 35.166667 & Japan & 1984-1987 & 4 & 114 & 883 & 100662 & Transects & Phytocentric & Quantitative\\
\addlinespace
Inouye 1988 & 148.266667 & -36.45 & Australia & 1983-1984 & 1 & 40 & 85 & 3400 & Plots & Phytocentric & Quantitative\\
\addlinespace
\rowcolor{gray!6}  Kaiser-Bunbury 2009 & 57.443254 & -20.452076 & Republic of Mauritius & 2003-2004 & 2 & 96 & 184 & 17664 & Plots & Phytocentric & Quantitative\\
\addlinespace
Kaiser-Bunbury 2014 & 55.43333 & -4.666667 & Republic of Seychelles & 2007-2008 & 6 & 37 & 341 & 12617 & Transects & Phytocentric & Quantitative\\
\addlinespace
\rowcolor{gray!6}  Kato 2000 & 129.493741 & 28.377248 & Japan & 1996-1999 & 16 & 110 & 609 & 66990 & Transects & Phytocentric & Quantitative\\
\addlinespace
Kevan 1970 & -71.3 & 81.816667 & Canada & 1967 & 1 & 20 & 91 & 1820 & Randow census walks & Phytocentric & Qualitative\\
\addlinespace
\rowcolor{gray!6}  Lundgren 2005 & -52 & 71 & Greenland & 2002 & 1 & 17 & 26 & 442 & Randow census walks & Phytocentric & Quantitative\\
\addlinespace
Olesen 2002 1 & 57.43 & -20.25 & Republic of Mauritius & 1998-1999 & 1 & 17 & 26 & 442 & Plots & Phytocentric & Quantitative\\
\addlinespace
\rowcolor{gray!6}  Mcmullen 1993 & -90.600747 & -0.290164 & Ecuador & NA & All islands & 105 & 54 & 5670 & - & Phytocentric & Qualitative\\
\addlinespace
Bartomeus 2008 & 3.296797 & 42.315336 & Spain & 2005 & 3 & 13 & 37 & 481 & Plots with transects & Phytocentric & Quantitative\\
\addlinespace
\rowcolor{gray!6}  Primack 1983 1 & 171.566667 & -42.95 & New Zealand & 1976-1978 & 1 & 18 & 60 & 1080 & Randow census walks & Phytocentric & Qualitative\\
\addlinespace
Primack 1983 2 & 171.78466 & -43.02823 & New Zealand & 1976-1978 & 1 & 41 & 139 & 5699 & Randow census walks & Phytocentric & Qualitative\\
\addlinespace
\rowcolor{gray!6}  Primack 1983 3 & 171.720224 & -43.099531 & New Zealand & 1976-1978 & 1 & 49 & 118 & 5782 & Randow census walks & Phytocentric & Qualitative\\
\addlinespace
Ramirez 1989 & -61.716667 & 5.583333 & Venezuela & NA & 1 & 48 & 49 & 2352 & Randow census walks & Phytocentric & Qualitative\\
\addlinespace
\rowcolor{gray!6}  Ramirez 1992 & -67.416667 & 8.933333 & Venezuela & 1983,1984,1989 & 1 & 28 & 53 & 1484 & Randow census walks & Phytocentric & Qualitative\\
\addlinespace
Robertson 1929 & -89.8968771 & 39.278958 & United States & 1997-1899 & NA & 456 & 1044 & 476064 & - & Phytocentric & Qualitative\\
\addlinespace
\rowcolor{gray!6}  Small 1976 & -75.5 & 45.4 & Canada & 1973 & 1 & 13 & 34 & 442 & 10h per spp & Phytocentric & Quantitative\\
\addlinespace
Souza 2018 & -57.885 & -21.701111 & Brazil & 2008-2009 & 1 & 62 & 89 & 5518 & Plots & Phytocentric & Quantitative\\
\addlinespace
\rowcolor{gray!6}  Traveset 2013 & -91.012863 & -0.6907 & Ecuador & 2010-2011 & 1 & 60 & 220 & 13200 & Randow census walks & Phytocentric & Quantitative\\
\addlinespace
Bartomeus 2015 unp. & -6.16895 & 37.234966 & Spain & 2015 & 16 & 57 & 277 & 15789 & Transects & Phytocentric & Quantitative\\
\addlinespace
\rowcolor{gray!6}  Bek 2006 & 10.216667 & 56.066667 & Denmark & 2003 & 1 & 37 & 225 & 8325 & Plots & Phytocentric & Qualitative\\
\addlinespace
Olesen 2002 2 & -31 & 39.4 & Azores & 2000 & 1 & 10 & 12 & 120 & Plots & Phytocentric & Quantitative\\
\addlinespace
\rowcolor{gray!6}  Bundgaard 2003 & 10.233333 & 56.066667 & Denmark & 2003 & 1 & 16 & 44 & 704 & Plots & Phytocentric & Qualitative\\
\addlinespace
Chacoff 2011 & -68.015892 & -32.008985 & Argentina & 2006-2009 & 4 & 59 & 196 & 11564 & Plots & Phytocentric & Quantitative\\
\addlinespace
\rowcolor{gray!6}  Dicks 2002 & 1.575532 & 52.762395 & England & 2001? & 2 & 23 & 80 & 1840 & Plots & Phytocentric & Quantitative\\
\addlinespace
Dupont 2009 & 9.1 & 6.1 & Denmark & 2005 & 2 & 31 & 329 & 10199 & Plots & Phytocentric & Quantitative\\
\addlinespace
\rowcolor{gray!6}  Elberling 1999 & 18.5 & 68.35 & Sweden & 1994 & 1 & 24 & 118 & 2832 & Plots with transects & Phytocentric & Quantitative\\
\addlinespace
Dupont 2009 2 & -20.5 & 74.5 & Greenland & 1996-1997 & 1 & 31 & 76 & 2356 & Random census walks & Phytocentric & Qualitative\\*
\end{longtabu}
\endgroup{}
\end{landscape}

@@

\textbf{PLOT 2}

@@

\#REFERENCES

\hypertarget{refs}{}
\leavevmode\hypertarget{ref-noreika2019pollinator}{}%
Noreika, Norbertas, Ignasi Bartomeus, Marie Winsa, Riccardo Bommarco,
and Erik Öckinger. 2019. ``Pollinator Foraging Flexibility Mediates
Rapid Plant-Pollinator Network Restoration in Semi-Natural Grasslands.''
\emph{Scientific Reports} 9 (1). Nature Publishing Group: 1--11.
